\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Win a bit of space

    \draw[out=-90,in=90,double,-implies,double equal sign distance] (0,5) to node[sloped, yshift =.7em]{\small Contextual equivalence preservation} (0,1);
  \end{tikzpicture}
  \caption{Proving one direction of fully abstract compilation (contextual equivalence preservation).}
  \label{fig:fa-proof-sketch}
\end{figure}

>>>>

    \draw[out=-90,in=90,double,-implies,double equal sign distance] (0,5) to node[sloped, yshift =.7em]{\Small Contextual equivalence preservation} (0,1);
  \end{tikzpicture}
  \caption{Proving one direction of fully abstract compilation (contextual equivalence preservation).}
  \label{fig:fa-proof-sketch}
\end{figure}
